better title eventually

### 2015-05-11 cs261n-paper/paper.tex
shuffled around sections

% is the abstract missing some oomph? 
% I don't know how much the storyline is showing through.. or what we are testing. 
\begin{abstract}
\indent \indent It is easy to drastically overestimate user comprehension 
and therefore be misguided for user behavior. 
Even though people download and install things all the time, 
they do not know how to do it securely, and worse, 
they are habituated into doing it a certain way. 
What users had trouble with were the most basic tasks, 
such as downloading and installing Tor, rather than 
nagivating a robust menu or understanding subtleties of security guarentees. 
This is really troubling, and matters for things like Tor. 
We use this insight to fix a bunch of stuff and also 
present a new experiment with a basic enough focus, 
making us the first to focus on censorship too. 
\end{abstract}

\section{Introduction} %this should CLEARLY state the results. 
\indent \indent Talk about the results and contributions concretely.
As short as possible summary of UX sprint here. %only what is necessary to understand results. 
Talk about the changes resulted in the Tor browser here.
As short as possible summary of lessons learned, 
and also a short as possible motivation for censorship work here. %yep, same.
Talk about the experiment design quickly here.

\section{Background}  %ramp people up!

\subsection{Tor} 
\indent \indent Talk about anything relevant to Tor. Just enough background so
that people who have never heard of it will know what I am talking
about, but no more than that.

\subsection{User behavior}
\indent \indent Then also talk about any of the behaviors we are trying to mitigate,
or talk about the average user and what they know, how they are motivated,
just sketching out the environment in general.

\subsection{Usable security impact} 
\indent \indent cite work which has made a huge impact on how people use it, and 
other things which still remain broken because of usability issues.

@@

\subsection{Censorship} 
\indent \indent Motivational paragraph time about how this is so everywhere.

@@

\section{UX sprint} 
\indent \indent Talk about it just enough that it makes a good storyline for the experiment that we 
are proposing a design of. Motivate it a little bit, and tell a story.

@@

\subsection{Impact}
\indent \indent whoo talk about the cool stuff that happened next here. 
This means talking about the tickets and changes made 
to the Tor browser, the start of a user manual, and 
increased Tor UX efforts as a whole.

\subsection{Takeaways} 
\indent \indent highlight what we learned and use this to transition into 
the design of the next experiment.

Wanted reproducibility of experiment.
Wanted more people for a representative population. 
Also make practical considerations such as avoiding transcription.

@@

\subsection{Motivation}
 talk about the generalizability of the work, what we aim to find, and what future work this will lead to. Be sure to sketch the storyline of honing in on specific features.

Tor has grown beyond its original purpose as and has 
since become an important Internet circumvention tool.
We specifically examine it usability as a censorship circumvention tool,
an essential facet for adoption and use.  
We focus our analysis on the connection configuration dialog of Tor browser,
as censorship circumvention requires correct transport configurations. %%
This study is aimed at evaluating 
if and how easily users can circumvent censorship using Tor Browser,
isolating specific browser features to study in the process. 
To this end, we will conduct a large-scale user study examining hundreds of users 
on how they navigate Tor's configuration wizard to complete seven browsing tasks 
in three different adversarial settings.

\subsection{What is Required of Users}
\indent \indent For users to circumvent censorship in their resident countries, they will need to configure Tor to set up a proxy, bridge, or both. There is a configuration wizard to help guide users through setting up their connection, but our hypothesis is that the average user will not easily be able to configure Tor correctly in these adverse settings, as they require the user to provide IP addresses of proxies or bridges to use. The goal of our experiment is to see how successful users are at carrying out common browsing tasks in an adversarial setting using Tor.

@@

\indent \indent Our experiment consists of three parts: informing and motivating the participants in order 
to roleplay in the experiment, asking our participants to complete a set of web browsing tasks which will 
require them to circumvent censorship using the Tor Browser, and soliciting feedback from our participants
about their experience. With participants' consent, we will also record their computer screen to monitor 
their activity and employ a browser extension to take empirical measurements (such as idle waiting time, 
how fast a particular task was completed, etc.) throughout the duration of this experiment.

@@

\indent \indent We plan to recruit up to 200 users for the purpose of this study, making this the largest user 
study to date examining Tor. We do this in order to increase our chances at recruiting a diverse
user population, ranging in age, gender, technical fluency, and other characteristics. Since Tor 
does not keep information regarding its user base, we will try to obtain a user base representative of
the average Internet using-population. Additionally, recruiting a large number of participants has the 
benefit of ensuring enough samples in order to have significant effect sizes in 
each simulated censorship environment.

This study will be conducted at the Experimental Social Science Laboratory (Xlab)
at the University of California, Berkeley. Recruitment will be conducted through Craigslist. 
Although Xlab provides a portal in which researchers can recruit a pre-registered user base,
we choose to not recruit through this portal, as their participants mostly consist of mostly Berkeley 
students. The laboratory setting consists of 36 Toshiba Tecra R850 laptops with cubicle walls 
separating each laptop. Since we do not have the ability to employ network-level firewalls in this
laboratory setting, we will use individual host firewalls to simulate the censorship environments.  
We will write and employ a browser extension will record user activity, such as how many times they 
clicked, what websites they were successfully able to visit, and how long they took to complete 
each task. This is because WHY? %ask david exactly why--technically. isn't the first hop in the clear?

@@

\section{Related Work} %this is distracting to have earlier. %don't overdo the citations. 
The stopping points paper on Tor's usability ~\cite{norcie2012eliminating}. 
And that is pretty much it for Tor usability stuff. %find more if it exists

@@

\section{Conclusion} 
Do not repeat the abstract, introduction, or the results section. 
Focus this time to discuss the limitations of the work and broader impacts.

Reach out to the community to make a call for more a focus on usability for security products.

>>>>

% is the abstract missing some oomph? 
% I don't know how much the storyline is showing through.. or what we are testing. 
\begin{abstract}
\indent \indent Tor has grown beyond its original purpose and has  since become an important 
Internet circumvention tool. We specifically examine it usability as a censorship circumvention tool, 
an essential facet for adoption and use.  We focus our analysis on the connection configuration dialog of 
Tor browser, as censorship circumvention requires correct transport configurations. 
This study is aimed at evaluating if and how easily users can circumvent censorship using Tor Browser,
isolating specific browser features to study in the process.  To this end, we present the design of
 a large-scale user study examining hundreds of users  on how they navigate Tor's configuration wizard to complete seven browsing tasks in three different adversarial settings. The experiment is scheduled for August 2015.
\end{abstract}

\section{Introduction} %%% 
\indent \indent Talk about the results and contributions concretely.
As short as possible summary of UX sprint here. %only what is necessary to understand results. 
Talk about the changes resulted in the Tor browser here.
As short as possible summary of lessons learned, 
and also a short as possible motivation for censorship work here. %yep, same.
Talk about the experiment design quickly here.

what we want to contribute to the research community.

\subsection{Tor} %%% 
\indent \indent Talk about anything relevant to Tor. Just enough background so
that people who have never heard of it will know what I am talking
about, but no more than that.

@@

\subsection{Censorship} %%%
\indent \indent Motivational paragraph time about how this is so everywhere.

\subsection{What is Required of Users} %%%
\indent \indent For users to circumvent censorship in their resident countries, they will need to 
configure Tor to set up a proxy, bridge, or both. The requirement of the user will vary on their censorship
environment, specifically, if they need to conceal the fact that they are using Tor or if Tor entry nodes 
have been blocked by the government.

There is a configuration wizard to help guide users through setting up their connection, but our hypothesis is that the average user will not easily be able to configure Tor correctly in these adverse settings, as they require the user to provide IP addresses of proxies or bridges to use. The goal of our experiment is to see how successful users are at carrying out common browsing tasks in an adversarial setting using Tor.

@@

\section{UX sprint}  %%%%
\indent \indent Talk about it just enough that it makes a good storyline for the experiment that we 
are proposing a design of. Motivate it a little bit, and tell a story.

@@

It is easy to overestimate user comprehension and therefore be 
misguided for user behavior. Even though people download and install things all the time, 
they do not know how to do it securely, and worse, they are habituated into doing it in the 
insecure manner. Of course, this is because the average user's objective is not security. 
For instance, most of our participants thought the download source was a legitimate site because
of the look and feel of the site and none our our participants thought to verify the download, 
even though there were clear instructions to do so on the download page.

During this pilot, the users were struggling with confusing bugs, such as flash errors which
say ``Firefox'' rather than ``Tor,'' disappearing buttons on the configuration window, and errors when
launching Tor from the download dialog rather than from their applications folder. This resulted in our 
participants spending most of their time on the download and install tasks, rather than 
navigating a robust menu or questioning the clarity of provided security guarantees.

\subsection{Impact}
\indent \indent Along with the Tor developers who came to observe the UX pilot, we filed 
a total of sixteen bug tickets to Tor. At the time of  this writing, eight of the sixteen tickets 
have already been resolved, and more will be resolved in the future.  The list of bug
tickets filed can be found at \url{https://trac.torproject.org/projects/tor/query?keywords=~uxsprint2015}.

As of April, the changes resulting from our pilot study has been incorporated into the latest 
version of Tor Browser, making Tor more usable for people to use. 
The summary of the usability changes can be found at \url{https://blog.torproject.org/blog/tor-browser-45a4-released}.

Through the publicity of this usability pilot study on the Tor weekly blogs, we were connected
with a source from the Library Freedom Project, which provides training on various technologies 
to libraries across the country. We now collaborate with her work on creating a user manual
for the Tor Browser.

\subsection{Takeaways} 
\indent \indent During the pilot study, we were attempting to test out a comprehensive set of 
features for the Tor Browser. Our users had difficulties completing all the given tasks in the 
time alloted for the experiment. Additionally, user fatigue was very evident, with users not 
engaging in the later set of tasks after being tired from the download and install process. 
To ensure that the experiment does not cause user fatigue, we select a smaller set of features 
as the target for the full-scale study.  After deliberating with Tor developers, and testing out
various features on our own, we chose to focus on the Tor Browser connection configuration 
dialog because of its crucial role in censorship circumvention.

Although the data from the pilot study provided a lot of insight into what users thought processes
are when completing various asks, transcribing audio recordings and syncing them to videos was
required a lot of manual labor. Not only did this form of data collection and processing not scale 
to larger numbers, we found that most users encountered similar thought processes and struggled
with the same issues. Because of this, we aim to collect our future qualitative data in the form of 
an open-ended survey question rather than using audio recordings.

While our pilot was insightful, the experiment itself is not very reproducible, as it requires
a specific target audience (journalists who have recently reported in other countries) along 
with specific guidance and feedback on how to perform a cognitive walkthrough. This makes it hard
for the research community to prove or build on any findings. Therefore, we take precautions
to ensure that our full-scale study will be reproducible.

@@

\subsection{Overview} %%%
Our experiment consists of three parts: informing and motivating the participants in order 
to roleplay in the experiment, asking our participants to complete a set of web browsing tasks which will 
require them to circumvent censorship using the Tor Browser, and soliciting feedback from our participants
about their experience. With participants' consent, we will also record their computer screen to monitor 
their activity and employ a browser extension to take empirical measurements (such as idle waiting time, 
how fast a particular task was completed, etc.) throughout the duration of this experiment.

@@

\subsection{Recruitment}  
\indent \indent We plan to recruit up to 200 users for the purpose of this study, making this the largest user 
study to date examining Tor. We do this in order to increase our chances at recruiting a diverse
user population, ranging in age, gender, technical fluency, and other characteristics. Since Tor 
does not keep information regarding its user base, we will try to obtain a user base representative of
the average Internet using-population. Additionally, recruiting a large number of participants has the 
benefit of ensuring enough samples in order to have significant effect sizes in 
each simulated censorship environment.

 %% what we will recruit for, how we inform, and interactions.

@@

\indent\indent This study will be conducted at the Experimental Social Science Laboratory (Xlab)
at the University of California, Berkeley. Recruitment will be conducted through Craigslist. 
Although Xlab provides a portal in which researchers can recruit a pre-registered user base,
we choose to not recruit through this portal, as their participants mostly consist of mostly Berkeley 
students. The laboratory setting consists of 36 Toshiba Tecra R850 laptops with cubicle walls 
separating each laptop. Since we do not have the ability to employ network-level firewalls in this
laboratory setting, we will use individual host firewalls to simulate the censorship environments.  
We will write and employ a browser extension will record user activity, such as how many times they 
clicked, what websites they were successfully able to visit, and how long they took to complete 
each task. This is because WHY? %ask david exactly why--technically. isn't the first hop in the clear?

@@

\section{Related Work} %%%
%%%Tor
The stopping points paper on Tor's usability ~\cite{norcie2012eliminating}. 
And that is pretty much it for Tor usability stuff. %find more if it exists

@@

%%%User behavior
\indent \indent Then also talk about any of the behaviors we are trying to mitigate,
or talk about the average user and what they know, how they are motivated,
just sketching out the environment in general.

%%% Other Usability stuff 
\indent \indent cite work which has made a huge impact on how people use it, and 
other things which still remain broken because of usability issues.
